Mock community evaluation

### 2022-03-24 06--mock_community.Rmd
create plot of mock comm read prop for reviewer

and I can add which reference sequence each asv was assigned to and its PID as seperate columns for easy use afterwards.

@@

```{r}
rps10_align_data <- align_mock_comm_seqs(asv_data, 'rps10', rps10_ref_data)
as.data.frame(filter_to_top_mc_ref_hits(rps10_align_data))
```

@@

```{r}
its_align_data <- align_mock_comm_seqs(asv_data, 'ITS', its_ref_data)
as.data.frame(filter_to_top_mc_ref_hits(its_align_data))
```

>>>>

and I can add which reference sequence each asv was assigned to and its PID as separate columns for easy use afterwards.

@@

```{r}
rps10_align_data <- align_mock_comm_seqs(asv_data, 'rps10', rps10_ref_data)
(rps10_best_mc_hits <- as.data.frame(filter_to_top_mc_ref_hits(rps10_align_data)))
```

@@

```{r}
its_align_data <- align_mock_comm_seqs(asv_data, 'ITS', its_ref_data)
(its_best_mc_hits <- as.data.frame(filter_to_top_mc_ref_hits(its_align_data)))
```

We can plot this to check how even the read depth is for each locus:

```{r}
rps10_best_mc_hits$abund <- rps10_best_mc_hits$abund / sum(rps10_best_mc_hits$abund)
its_best_mc_hits$abund <- its_best_mc_hits$abund / sum(its_best_mc_hits$abund)
plot_data <- rbind(mutate(rps10_best_mc_hits, locus = "Rps10"), mutate(its_best_mc_hits, locus = "ITS1"))
mc_read_prop_plot <- plot_data %>%
  ggplot(aes(x = locus, y = abund)) +
  geom_boxplot() +
  geom_hline(yintercept=1/24, linetype="dashed") +
  labs(x = "Locus", y = "Read Proportion")
mc_read_prop_plot
ggsave(mc_read_prop_plot, filename = 'read_proportion_of_mock_community.pdf', path = file.path('results'), width = 5, height = 5)
```

Standard deviation:

```{r}
sd(rps10_best_mc_hits$abund)
sd(its_best_mc_hits$abund)
```

We can also look at if the proportion of sequences in correlated

```{r}
plot_data %>%
  pivot_wider(names_from = locus, values_from = abund) %>%
  ggplot(aes(x = Rps10, y = ITS1)) +
  geom_point()
```
